---
title: "data_cleaning"
#output: html_notebook
---
# PA Data Cleaning

## Clear environment
```{r}
rm(list = ls(all = TRUE))
```

## Define User
```{r}
# User="Matias"
User = "Sarah"
# User="Abbey"

if (!exists('handl_OneDrive'))
{
  if (User == "Matias")
    source(
      'C:/Users/myb/OneDrive - Department of Primary Industries and Regional Development/Matias/Analyses/SOURCE_SCRIPTS/Git_other/handl_OneDrive.R'
    )
  if (User == "Sarah")
    handl_OneDrive = function(x)
      paste('C:/Users/S.Jesso/Documents/GitHub', x, sep = '/')
  if (User == "Abbey")
    handl_OneDrive = function(x)
      paste(
        'C:/Users',
        Usr,
        'OneDrive - Department of Primary Industries and Regional Development/Matias',
        x,
        sep = '/'
      )
}
```

## Load Packages
```{r}
library(tidyverse)
library(rlang)
library(MASS)
library(janitor)
library(lazyeval)

options(stringsAsFactors = FALSE,dplyr.summarise.inform = FALSE) 
```

## Source Constants and Functions
```{r}
source("data_cleaning_functions.R")
source("data_cleaning_constants.R")
```

# Underwater
## Define Data Dump
```{r}
Event.Mes.data.dump <- 'Abbey_Sarah'
```

## Loop to read in and clean data
```{r}
if(Event.Mes.data.dump=='Abbey_Sarah')
{
  #1. read in  data
  #1.1. gillnet
  setwd(
    'C:/Users/S.Jesso/OneDrive - Department of Primary Industries And Regional Development/Final_EMobs/EMOutputs/Gillnet'
  )
  filenames <- list.files(pattern = '*.csv')
  dummy.GN <- lapply(filenames, read.csv, skip = 4)
  #1.2. longline
  setwd(
    'C:/Users/S.Jesso/OneDrive - Department of Primary Industries And Regional Development/Final_EMobs/EMOutputs/Longline'
  )
  filenames <- list.files(pattern = '*.csv')
  dummy.LL <- lapply(filenames, read.csv, skip = 4)
  
  #2. put data in standard format
  #2.1. gillnet
  Video.net.interaction = Video.net.maxN = Video.net.obs = vector('list', length(dummy.GN))
  
  for (i in 1:length(dummy.GN))
  {
    dummy.GN[[i]] <- RenameColumn(dummy.GN[[i]])
    if (!'Position' %in% names(dummy.GN[[i]]))
    dummy.GN[[i]]$Position = NA
    Video.net.interaction[[i]] <- dummy.GN[[i]] %>%
      filter(is.na(MaxN)) %>%
      CategoriseComment() %>%
      dplyr::select(all_of(interaction.names)) %>%
      mutate(
        Number = ifelse(Number == 'AD', NA, Number),
        No.haul = Alt.species == "no haul",
        No.fish = Alt.species == "no fish",
        Species = ApplySpecies(Species, Alt.species),
        Escape = ifelse(
          grepl("^\\d|^\\<", Escape),
          gsub("([0-9]+).*$", "\\1", Escape),
          ''),
        Method = "Gillnet",
        Interaction = AssignInteractions(Interaction)
      ) 
    
    Video.net.maxN[[i]] <- dummy.GN[[i]] %>%
      RenameColumn() %>%
      CategoriseComment() %>%
      dplyr::select(all_of(maxn.names)) %>%
      mutate(
        Species=ApplySpecies(Species, Alt.species),
        Method = "Gillnet",
        )
      
    Video.net.obs[[i]] = dummy.GN[[i]] %>%
      RenameColumn() %>%
      CategoriseComment() %>%
      mutate(
        observation = Alt.species,
        No.haul = Alt.species == "no haul",
        No.fish = Alt.species == "no fish",
        code = Code,
        Method = "Gillnet"
      ) %>%
      dplyr::select(all_of(observation.names))
  }
  
  Video.net.interaction <- do.call(rbind, Video.net.interaction) %>%
    filter(!Species %in% c("", " ") &
             No.haul == FALSE & No.fish == FALSE)
  Video.net.maxN = do.call(rbind, Video.net.maxN) %>%
    filter(!is.na(MaxN))
  Video.net.obs = do.call(rbind, Video.net.obs) %>%
    filter(!observation == '')
  
  #2.2. longline
  Video.longline.interaction = Video.longline.maxN = Video.longline.obs =
    vector('list', length(dummy.LL))
  for (i in 1:length(dummy.LL))
  {
    dummy.LL[[i]] <- RenameColumn(dummy.LL[[i]])
    if (!'Position' %in% names(dummy.LL[[i]]))
      dummy.LL[[i]]$Position = NA
    Video.longline.interaction[[i]] <-  dummy.LL[[i]] %>%
      filter(is.na(MaxN)) %>%
        CategoriseComment() %>%
      dplyr::select(all_of(interaction.names)) %>%
      mutate(
        Number = ifelse(Number == 'AD', NA, Number),
        No.haul = Alt.species == "no haul",
        No.fish = Alt.species == "no fish",
        Species=ApplySpecies(Species, Alt.species),
        Method = "Longline",
        Escape = ifelse(
          grepl("\\d", Escape),
          gsub("([0-9]+).*$", "\\1", Escape),
          ''
        ),
        Interaction = AssignInteractions(Interaction)
      )
    
    Video.longline.maxN[[i]] = dummy.LL[[i]] %>%
      RenameColumn() %>%
       CategoriseComment() %>%
      dplyr::select(all_of(maxn.names)) %>%
      mutate(
        Method = "Longline",
        Species=ApplySpecies(Species, Alt.species)
        )
    
    Video.longline.obs[[i]] = dummy.LL[[i]] %>%
      RenameColumn() %>%
      CategoriseComment() %>%
      mutate(
        observation = Alt.species,
        No.haul = Alt.species == "no haul",
        No.fish = Alt.species == "no fish",
        code = Code,
        Method = "Longline"
      ) %>%
      dplyr::select(all_of(observation.names))
  }
  Video.longline.interaction = do.call(rbind, Video.longline.interaction) %>%
    filter(!Species %in% c(" ", "") &
             No.haul == FALSE & No.fish == FALSE)
  Video.longline.maxN = do.call(rbind, Video.longline.maxN) %>%
    filter(!is.na(MaxN)) %>%
    rename(Max.N = MaxN)
  Video.longline.obs = do.call(rbind, Video.longline.obs) %>%
    filter(!observation == '') %>%
    rename(Observation = observation,
           optcode = OpCode)
  
  
}

```
## Checks
```{r}
llchecklist <- subset(Video.longline.interaction, is.na(Species) & No.haul==FALSE & No.fish==FALSE)
llchecklist
```
```{r}
sp.in.net.inter <- unique(Video.net.interaction$Species)
sp.in.net.inter
```
```{r}
sp.in.ll.inter <- unique(Video.longline.interaction$Species)
sp.in.ll.inter
```
```{r}
countopcodesll <- as.list(unique(Video.longline.interaction$OpCode))
length(countopcodesll)
### SHOULD BE 156 and unique sp in vli should have octopus
```
```{r}
sp.in.ll.maxn <- unique(Video.longline.maxN$Species)
sp.in.ll.maxn
```

```{r}
llmaxncheck <- subset(Video.longline.maxN, Species==""|is.na(Species))
llmaxncheck
```
```{r}
sp.in.net.maxn <- unique(Video.net.maxN$Species)
sp.in.net.maxn
```
```{r}
gnmaxncheck <- subset(Video.net.maxN, Species==""|is.na(Species))
gnmaxncheck
```
# check to compare unique sp in inter and maxn dfs
## Alt species such as snail, turtle, bird are OK.
```{r}
setdiff(sp.in.ll.inter, sp.in.ll.maxn)
setdiff(sp.in.ll.maxn, sp.in.ll.inter)
```
```{r}
check.net.maxn <- setdiff(sp.in.net.inter, sp.in.net.maxn)
check.net.maxn
checklist.net.maxn <- Video.net.maxN %>% filter(Species=="mosaica")
checklist.net.maxn
```
```{r}
check.net.maxn.2 <- setdiff(sp.in.net.maxn, sp.in.net.inter)
check.net.maxn.2
```
## List of points that have no interaction assigned
```{r}
gn.no.interaction <- Video.net.interaction %>% filter(Interaction == "Missing data")
gn.no.interaction
unique(gn.no.interaction$Species)
crap <- gn.no.interaction %>% filter(Species=="baitfish")
unique(crap$OpCode)
## Alt species are OK
```
```{r}
ll.no.interaction <- Video.longline.interaction %>% filter(Interaction == "Missing data")
ll.no.interaction
unique(ll.no.interaction$Species)
crap1 <- ll.no.interaction %>% filter(Species%in%c("baitfish"))
unique(crap1$OpCode)
```
# Observation df check
```{r}
obs.gn.check <- unique(Video.net.obs$observation)
obs.gn.check
```
```{r}
obs.ll.check <- unique(Video.longline.obs$Observation)
obs.ll.check
```
# List EMobs to check
```{r}
checklist <- c(
               "Albany_Longline_PA0113_Camera_#8_Plectorhinchus_caeruleonothus_unlikely"
               )
```

# Deck 2
```{r}
  setwd(
    'C:/Users/S.Jesso/OneDrive - Department of Primary Industries And Regional Development/Final_EMobs/Deck/OutputDeck2/23-01-23'
  )
# Read in data
dummy.d2 <- list()  
deck2filenames <- dir(pattern="*.csv")
  
  for (i in 1:length(deck2filenames))
  {
    dummy.d2[[i]] <- read.csv(deck2filenames[i], skip=4)
  }
# Clean with User Defined functions
Deck.2.fish <-  Deck.2.obs <-  vector('list', length(dummy.d2))
 for (i in 1:length(dummy.d2))
  {
   Deck.2.fish[[i]] <- dummy.d2[[i]] %>% 
     DeckTwoColumns() %>% 
      RemoveWhitespace(hooklocation, hookloc.and.comments) %>% 
      rename(`hook distance to float/weight`=hooklocation) %>% 
      HookLocation() %>% 
     CategoriseGaffed() %>%
     CategoriseDropout() %>% 
      separate("Curtin opcode", c("Region", "DPIRD code", "Position"), sep="_", remove=FALSE) %>% 
     CategoriseRegion() %>% 
     mutate(Position = "Deck#2",
            Species=ApplySpecies(Species, Alt.species)) %>% 
      dplyr::select(all_of(deck.2.fish.names)) 
 }

Deck.2.fish <- do.call(rbind, Deck.2.fish)
```
# Checks
```{r}
table(Deck.2.fish$Region, Deck.2.fish$Position
      )
```
```{r}
table(Deck.2.fish$gaffed, Deck.2.fish$dropout)
```
```{r}
table(Deck.2.fish$depredated)
```
```{r}
table(Deck.2.fish$Alt.species)
```
```{r}
table(Deck.2.fish$`hook distance to float/weight`)
```
```{r}
unique(Deck.2.fish$Species)
```


# Deck 1
```{r}
  setwd(
    'C:/Users/S.Jesso/OneDrive - Department of Primary Industries And Regional Development/Final_EMobs/EMoutputs/Deck1'
  )
# Read in data
dummy.d1 <- list()  
deck1filenames <- dir(pattern="*.csv")
  for (i in 1:length(deck1filenames))
  {
    dummy.d1[[i]] <- read.csv(deck1filenames[i], skip=4)
  }
Deck.1.fish <-  Deck.1.habitat <-  vector('list', length(dummy.d1))
 for (i in 1:length(dummy.d1))
  {
   Deck.1.fish[[i]] <- dummy.d1[[i]] %>%
    DeckOneColumns() %>%
    separate("curtin opcode", c("Region", "DIPRD code", "Position"), sep="_", remove=FALSE) %>%
     CategoriseRegion() %>% 
     CategoriseCondition() %>% 
     CategoriseRetained() %>% 
     CategoriseMeshed() %>% 
     mutate(Position = "Deck#1",
            Species=ApplySpecies(Species, Alt.species)) %>%
     filter(is.na(`Percentage cover`)) %>% 
    dplyr::select(all_of(deck.1.fish.names))

Deck.1.habitat[[i]] <- dummy.d1[[i]] %>%
  DeckOneColumns() %>%
  separate("curtin opcode", c("Region", "DIPRD code", "Position"), sep="_", remove=FALSE) %>%
  CategoriseRegion() %>% 
  mutate(
    `Curtin opcode` = `curtin opcode`
  ) %>% 
  CategoriseMeshed() %>% 
  filter(!is.na(`Percentage cover`)) %>%
dplyr::select(all_of(deck.1.habitat.names))
}
Deck.1.fish <- do.call(rbind, Deck.1.fish)
Deck.1.habitat <- do.call(rbind, Deck.1.habitat)
```
# Checks
```{r}
(d1.q <- unique(Deck.1.fish$Region))
(d1.w <- unique(Deck.1.fish$Position))
(d1.e <- unique(Deck.1.fish$Species))
(d1.r <- table(Deck.1.fish$condition))
(d1.t <- table(Deck.1.fish$retained))
(d1.y <- table(Deck.1.fish$meshed))
(d1.u <- unique(Deck.1.habitat$`Percentage cover`))
(d1.i <- table(Deck.1.habitat$Species))
```



# Subsurface
```{r}
  setwd(
    'C:/Users/S.Jesso/OneDrive - Department of Primary Industries And Regional Development/Final_EMobs/EMoutputs/Subsurface'
  )
# Read in data
dummy.ss <- list()  
ssfilenames <- dir(pattern="*.csv")
  for (i in 1:length(ssfilenames))
  {
    dummy.ss[[i]] <- read.csv(ssfilenames[i], skip=4)
  }
SS.fish <- vector('list', length(dummy.ss))
 for (i in 1:length(dummy.ss)){
   SS.fish[[i]] <- dummy.ss[[i]] %>%
     SSColumns() %>% 
     mutate(Region = str_extract(`DPIRD code`, "[^_]+"))
    # dplyr::select(all_of(subsurface.names)) %>% 
    print(i)
 }
#SS.fish <- do.call(rbind, SS.fish)
```

