---
title: "2021 Parks Australia Report"
author: "Matias Braccini"
date: "13/01/2021"
output:
  word_document:  
    toc: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "C:/Matias/Parks Australia/2019_project/Report to Parks Australia") })

---

```{=openxml}
<w:p><w:r><w:br w:type="page"/></w:r></w:p>
```
```{r globaloptions, include=FALSE}
knitr::opts_chunk$set(fig.width = 10,fig.height = 10,
                        echo = TRUE, warning=FALSE,message=FALSE)
```


## Socio-economic
From catch and effort data: report who is fishing (number of boats)
From Licence data: report who has licence/units, how many units, who’s transferring units by year, etc. Describe dynamics



## Introduction
Some text

<!-- global for setting path to figures -->
```{r, echo=FALSE}
PA.outpus='C:/Matias/Analyses/Parks Australia/outputs'
PA.historic=paste(PA.outpus,'Historic_catch_effort',sep='/')
```

<!-- 1. Overall catch compostion by method -->
```{r, echo=FALSE}
path=paste(PA.historic,'Catch_composition/Overall_GN_LL_overall_Monthly.tiff',sep='/')
```
![Figure X. Cumulative reported catch by method. Monthly records](`r path`){width=600px}
```{r, echo=FALSE}
path=paste(PA.historic,'Catch_composition/Overall_GN_LL_overall_Daily.tiff',sep='/')
```
![Figure X. Cumulative reported catch by method. Daily records](`r path`){width=600px}


```{r, echo=FALSE}
path=paste(PA.historic,'Catch_composition/Overall_GN_LL_by zone_Monthly.tiff',sep='/')
```
![Figure X. Cumulative reported catch by method and zone. Monthly records](`r path`){width=600px}
```{r, echo=FALSE}
path=paste(PA.historic,'Catch_composition/Overall_GN_LL_by zone_Daily.tiff',sep='/')
```
![Figure X. Cumulative reported catch by method and zone. Daily records](`r path`){width=600px}
